### 2017-01-31 local-capability-machine.tex
put old incomplete awkward example proof in comment
added lemma for memory satisfaction of static region
added lemma about data only memory and memory satisfaction for standard regions.

\begin{proof}[Proof of Lemma~\ref{lem:correctness-g1} (using scall)]

@@

@@

\lau{If $c_{g1}$ is global it seems like we will run into trouble. When we have to prove $\npair{c_{g1}} \in \stdvr(W)$ - for now g1 is global (then we will see if it gives any troubles later on)}

@@

>>>>

\begin{proof}[Proof of Lemma~\ref{lem:correctness-g1} (using \texttt{scall} lemma)]

@@

\begin{comment}

@@

\lau{If $c_{g1}$ is global it seems like we will run into trouble. When we have to prove $\npair{c_{g1}} \in \stdvr(W)$ - for now g1 is global (then we will see if it gives any troubles later on)}
\end{comment}

@@

\begin{lemma}[Memory satisfaction and static regions]
  \label{lem:mem-sat-static}
  \[
    \memSat{\ms}{[i \mapsto \iota^\sta(v,\ms)]}
  \]
\end{lemma}

\begin{lemma}[Data only memory and standard regions]
  \label{lem:mem-sat-data-only-std-regions}
  If
  \begin{itemize}
  \item $\forall \addr \in \dom(\ms)\ldotp \ms(a) \in \nats$
  \item $\iota \in \{\iota^\pwl,\iota^\nwl,\iota^{\nwl,p} \}$
  \end{itemize}
  then
  \[
    \memSat{\ms}{[i \mapsto \iota^\pwl(\dom(\ms))]}
  \]
\end{lemma}
